%-------------------------
% Resume in Latex
% Author : Sean Chou
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Sean Chou} \\ \vspace{5pt}
    \small
	\faMobile \hspace{.5pt} \href{tel:0975061890}{+886(0)975061890}
    $|$
    \faEnvelopeO \hspace{.5pt} \href{mailto:yschoou@gmail.com}{yshcoou@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/sean-chou-58631213/}{LinkedIn}
    $|$
    \faCaretSquareORight \hspace{.5pt} {Available to Start after 2024-Sept-30}
\end{center}



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ SystemVerilog, SVA, Verilog, C, assembly, Python, tcl, OCaml} \\ \vspace{3pt}
        
        \textbf{Methodologies:}{ UVM, formal verification, RIS/ISSCMP, portable stimulus } \\ \vspace{3pt}

        \textbf{Design Knowledge:}{ ARM/RISC-V CPU arch/uarch, cache coherency, USB} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Anshingtek}{Hsinchu, Taiwan}
      {Principal Manager}{Dec 2020 \textbf{--} Present}
        \resumeItemListStart
	    \resumeItem{ARM v9a small-core CPU IP co-DV Lead: 2022-2024 I lead around 40 DV engineers in our customer (ARM China) and Anshingtek, separated into 10 DV Units: 1 top level, 2 multi-unit level, 6 units and a formal team.}
	    \resumeItem{Anshingtek co-Engineer Manager (manage 20+ engineers) - host Anshingtek monthly all-hands since 2022-Jan.} 
	    \resumeItem{I created a tool to interpret ARMv9a ASL and deployed it to gem5 model, DPU/VPU/MMU DV and ISA Formal.} 
	    \resumeItem{I verified GIC CPU interface from zero to sign-off and FPU (MUL/FMA/DIV) formal equivalence w/ SoftFloat.} 
        \resumeItemListEnd

    \resumeSubheading
      {MediaTek. Inc}{Hsinchu, Taiwan}
      {Senior Manager (lead 28 people DV team)}{Mar 2018 \textbf{--} Dec 2020}
        \resumeItemListStart
	    \resumeItem{DV of In-house RISC-V cores (based on UVM and Spike model)}
                \resumeSubHeadingListStart
	\small{\item{ Core 1: 2-way 6 stages in-order pipeline processor. FPU, L1, branch predict, exception/interrupt, debug, trace.}}
	\small{\item{ Core 2: 3-way 8 stages with shared L2, vector extension and user defined extension. (only differences are listed)}}
                \resumeSubHeadingListEnd
    
	    \resumeItem{DV of an In-house cache coherency interconnect for v8.0a cores such as Cortex-A53 with snoop filter.}
	    \resumeItem{DV of Integrated ARM licensed CPU sub-system: multiple core scenarios based on portable stimulus.}
	    \resumeItem{DV of in-house DLA: data types conversion, convolution, activation, compression, flow controller.}
        \resumeItemListEnd

    \resumeSubheading
      {MediaTek. Inc}{Hsinchu, Taiwan}
      {Verification Methodology (CAD) Manager}{Mar 2013 \textbf{--} Mar 2018}
        \resumeItemListStart
	    \resumeItem{UVM/SV training, collaboration and deployment with needed teams such bus interconnect or ethernet switch.}
	    \resumeItem{Emulators: Palladium, Zebu, Veloce: porting, speed optimize, enable peripherals and management}
	    \resumeItem{In-house VIP/AIP and regression utilities (coverage, regression, permission management, CI)}
	    \resumeItem{Establish Power Aware (UPF) simulaiton flow for phone; static flow: formal/SVA, CDC, lint}
	    \resumeItem{DV related management: people, licenses, EDA collaboration, IT for LSF queue (machine slots).}
        \resumeItemListEnd

     \resumeSubheading
      {MediaTek. Inc}{Hsinchu, Taiwan}
      {Technical Manager}{June 2010 \textbf{--} Feb 2013}
        \resumeItemListStart
	    \resumeItem{USB 3.0 controller DV (2 DUT: xHCI Host and proprietary device): hands on and finish the 1st project (around 180 RTL bugs fixed in 10 months and make FPGA/Silicon mass production smoothly) then transfer to others.}
	    \resumeItem{In charge of H/W accelerators flow and successfully deploy Palladium to modem team.}
	    \resumeItem{Attend to DVCon 2012 and read all 2010-2011 DVCon Papers.}
        \resumeItemListEnd

      \resumeSubheading
      {Ambarella}{Hsinchu, Taiwan}
      {Researcher}{Nov 2009 \textbf{--} May 2010}
        \resumeItemListStart
	    \resumeItem{Self study OVM and coached 3 members to verify USB20 Device and NAND Flush Controller.}
        \resumeItemListEnd
   
      \resumeSubheading
      {Sunplus}{Hsinchu, Taiwan}
      {Technical Manager}{Jul 2002 \textbf{--} Oct 2009}
        \resumeItemListStart
	    \resumeItem{USB 1.0 controllers design from scratch alone. from read spec., understand the request from PCI-USB card, design RTL coding, setup FPGA environment, post-silicon validation, customer engagement.}
	    \resumeItem{Lead 3 people-team for 2 USB 2.0 designs: standard OHCI/EHCI host and dual-role proprietary design}
	    \resumeItem{Help to build a 14 people design/verification team in Chengdu at 2006. (they grew to 37 people in 2009) include recruiting/training/goal setting/tracking/review. (try to build DV to prevent bugs found by head quarter)}
        \resumeItemListEnd
 
  \resumeSubHeadingListEnd


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {National Chaio Tung University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Hsinchu, Taiwan}
      {Master's Degree in Electronics Engineering} {Sep 2000 \textbf{--} Jun 2002}
      {Bachelor of Engineering - BE, Electronics Engineering}{Sep 1996 \textbf{--} Jun 2000}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
